---
name: Valerio
surname: Gherardi
position: "Data Scientist"
address: "Valencia, España"
phone: +34 681 904 907
profilepic: me-circle-cropped.png
www: vgherard.github.io
email: "vgherard@sissa.it"
twitter: ValerioGherardi
github: vgherard
linkedin: vgherard
date: "Updated: `r format(Sys.Date())`"
aboutme: "Theoretical Physicist  | Data Scientist"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
Sys.setenv(LANG = "en_GB.UTF-8")
library(vitae)
library(tibble)
library(dplyr)
```

# Description

My background in Physics provides me with a strong scientific and analytic
mindset, that I enjoy applying to problems and challenges coming from different 
areas. I am currently employed as Data Scientist at Voicemod, a software development company whose main focus are voice changing technologies, which represents for 
me a tremendous opportunity for widening my experience with data in a cool and  fast-changing scenario.

During my PhD in Trieste I have had the privilege to study in an international, multicultural and multidisciplinary environment.
I love and get motivation from finding myself surrounded by people with heterogeneous backgrounds and life experiences.

What motivates me more in my work is being a concrete help to people 
and teams I collaborate with, and, on the personal side, getting the chance to 
learn something new every day.

# Work Experience
```{r}
tribble(
	~ Name, ~ Year, ~ Company, ~ Where,
	"Data Scientist", "2021-Current", "Voicemod", "Valencia, Spain"
	) %>%
	arrange(desc(Year)) %>%
	detailed_entries(
		what = Company, with = Name, # Swapped for better format!
		when = Year, where = Where
	)
```


# Education

```{r}
tribble(
	~ Name, ~ Year, ~ Institution, ~ Where, ~Details,
	"Laurea Triennale in Fisica", "2012-15", "Università La Sapienza", "Rome, Italy", "Final Grade: 110/110 cum laude",
	"Laurea Magistrale in Fisica", "2015-2017", "Università La Sapienza", "Rome, Italy", "Final Grade: 110/110 cum laude",
	"PhD in Theoretical Particle Physics", "2017-2021", "International School for Advanced Studies (SISSA)", "Trieste, Italy", "Awarded with honourable mention."
	) %>%
	arrange(desc(Year)) %>%
	detailed_entries(
		what = Institution, with = Name, # Swapped for better format!
		when = Year, where = Where, 
		why = Details
	)
```

# Technical Skills and Tool Stack

**Programming languages.** R / Python / C++ / Wolfram / FORTRAN

**SQL - DBMS** Amazon Redshift / Google BigQuery

**BI and visualization tools.** Tableau / Looker / Amplitude / RStudio Shiny / Plotly

**ETL.** DBT / Airflow

**Cloud Computing.** Amazon Web Services / Google Cloud Platform

**Machine Learning.** Keras / Tensorflow

**Scientific skills.** Mathematical and Statistical modeling / Machine and Deep Learning / Natural Language Processing / Algorithmic coding / Scientific Communication

# Language Skills

**Italian** Mother tongue | **English** Professional | **Spanish** Advanced

# Personal Projects

### `r2r` ([vgherard.github.io/r2r/](https://vgherard.github.io/r2r/)) {-}
Implementation of hash tables in the R programming language.

### `kgrams` ([vgherard.github.io/kgrams/](https://vgherard.github.io/kgrams/)) {-}
Tools for training and evaluating $k$-gram language models, R package with C++ backend. See also the associated blog post at [datascienceplus.com/an-introduction-to-k-gram-language-models-in-r/](https://datascienceplus.com/an-introduction-to-k-gram-language-models-in-r/). This software is currently awaiting for peer-review at [rOpenSci.org](https://ropensci.org/).

### `runiv` ([github.com/vgherard/runiv](https://github.com/vgherard/runiv)) {-}
An R client for R-universe APIs.

### `hepscrape` ([github.com/vgherard/hepscrape](https://github.com/vgherard/hepscrape))  {-}
An arXiv scraper built using R, Python and GitHub Actions. 

### `fcci` ([vgherard.github.io/fcci/](https://vgherard.github.io/fcci/)) {-}

Support for Feldman-Cousins Confidence Intervals; R/C++ implementation.

# Certifications

```{r}
tribble(
  ~ Name, ~ Year, ~ Institution, ~ Where, ~Details,
  "Data Structures and Algorithms Specialization", "2021", "University of California San Diego", "Coursera.org", "Course description and certificate: https://coursera.org/share/4fe6c2e914585cb813c93488d20d8f52",
  "Natural Language Processing Specialization", "2021", "deeplearning.ai", "Coursera.org", "Course description and certificate: https://coursera.org/share/903e270df65d75737d6c884743509e84",
  "Deep Learning Specialization", "2020", "deeplearning.ai", "Coursera.org", "Course description and certificate: https://coursera.org/share/1a79776ec145f7d140c93b95281f5250",
  "Data Science Specialization", "2020", "Johns Hopkins University", "Coursera.org", "Course description and certificate: https://coursera.org/share/3d64e7b0e1038f16fdb2103a71878e53"
  
) %>% 
  detailed_entries(
		what = Institution, with = Name, # Swapped for better format!
		when = Year, where = Where, 
		why = Details
	)
```

# Publications

```{r}
bibliography_entries("biblio.bib") %>%
  arrange(desc(issued))
```

# Awards

### *"Admeto Pettinari e Paolo Andreini" Scholarship* (01/10/2019){-}
Awarded by *Cassa di Sovvenzione e Risparmio per i dipendenti della Banca d'Italia* 
