---
name: Valerio
surname: Gherardi
position: "Data Scientist"
address: "Valencia, España"
phone: +34 681 904 907
profilepic: me-circle-cropped.png
www: vgherard.github.io
email: "vgherard840@gmail.com"
twitter: ValerioGherardi
github: vgherard
linkedin: vgherard
date: "Updated: `r format(Sys.Date())`"
# aboutme: "Theoretical Physicist  | Data Scientist"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
Sys.setenv(LANG = "en_GB.UTF-8")
library(vitae)
library(tibble)
library(dplyr)
```

# Description

I am a tireless student. My scientific background provides me with a strong 
analytic mindset, that I enjoy applying to problems and challenges coming 
from diverse areas. This is partly why, after completing my PhD in Particle 
Physics, I decided to steer myself in a new direction, 
and to pursue a career in Data Science - considering that this represented a 
great opportunity to keep doing what I like and do best, in a dynamic 
environment that fueled my curiosity.

What motivates me most in my day-to-day work is to bring data-driven business 
advice to my colleagues, and to enable teams to *measure* the impact of 
their efforts. On the personal side, I love getting the chance to learn some new 
trick every day.

# Work Experience
```{r}
tribble(
	~ Name, ~ Year, ~ Company, ~ Where,
	"Data Scientist - Product Analytics", "2021-Current", "Voicemod", "Valencia, Spain"
	) %>%
	arrange(desc(Year)) %>%
	detailed_entries(
		what = Company, with = Name, # Swapped for better format!
		when = Year, where = Where,
		why = "My main tasks involve experimental design and coordination of A/B tests, analysis of complex user behavioral data, inference and predictive modeling around product decisions. Working closely with the Content and Monetization teams, these analyses usually revolve around the optimisation of activation, engagement and financial KPIs. In addition to that, I often provide support for data-engineering and reporting needs, especially on the data-modeling front."
	)
```


# Education

```{r}
tribble(
	~ Name, ~ Year, ~ Institution, ~ Where, ~Details,
	"Laurea Triennale in Fisica", "2012-15", "Università La Sapienza", "Rome, Italy", "Final Grade: 110/110 cum laude",
	"Laurea Magistrale in Fisica", "2015-2017", "Università La Sapienza", "Rome, Italy", "Final Grade: 110/110 cum laude",
	"PhD in Theoretical Particle Physics", "2017-2021", "International School for Advanced Studies (SISSA)", "Trieste, Italy", "Awarded with honourable mention."
	) %>%
	arrange(desc(Year)) %>%
	detailed_entries(
		what = Institution, with = Name, # Swapped for better format!
		when = Year, where = Where, 
		why = Details
	)
```

# Technical Skills and Tool Stack

**Scientific skills.** Experimental Design / Statistical Modeling / Algorithmic Coding / Scientific Communication

**Programming languages.** R / Python / Bash / C++ / Wolfram / FORTRAN

**Database/Warehouse.** Snowflake / Redshift / BigQuery / SQLite / PostgreSQL

**Reporting and Visualization.** Tableau / Looker / Amplitude / RMarkdown / Shiny / Plotly / Streamlit

**Data Modeling and Engineering.** DBT / Airflow

**Data Platforms.** mParticle / split.io / Iterable

**Cloud Computing.** Google Cloud Platform / AWS / DigitalOcean

**Deep Learning.** Keras / Tensorflow

**Misc.** Git / Docker

# Language Skills

**Italian** Mother tongue | **English** Professional | **Spanish** Professional

# Personal Projects

Below are some fun-projects I have worked on - mostly focused on 
Statistics/Machine-Learning and developed in the R programming language.

### `kgrams` ([vgherard.github.io/kgrams/](https://vgherard.github.io/kgrams/)) {-}
Tools for training and evaluating $k$-gram language models, R package with C++ backend.

### `fcci` ([vgherard.github.io/fcci/](https://vgherard.github.io/fcci/)) {-}
Support for Feldman-Cousins Confidence Intervals; R/C++ implementation.

### `r2r` ([vgherard.github.io/r2r/](https://vgherard.github.io/r2r/)) {-}
Implementation of hash tables in the R programming language.

# Certifications

```{r}
tribble(
  ~ Name, ~ Year, ~ Institution, ~ Where, ~Details,
  "Data Structures and Algorithms Specialization", "2021", "University of California San Diego", "Coursera.org", "Course description and certificate: https://coursera.org/share/4fe6c2e914585cb813c93488d20d8f52",
  "Natural Language Processing Specialization", "2021", "deeplearning.ai", "Coursera.org", "Course description and certificate: https://coursera.org/share/903e270df65d75737d6c884743509e84",
  "Deep Learning Specialization", "2020", "deeplearning.ai", "Coursera.org", "Course description and certificate: https://coursera.org/share/1a79776ec145f7d140c93b95281f5250",
  "Data Science Specialization", "2020", "Johns Hopkins University", "Coursera.org", "Course description and certificate: https://coursera.org/share/3d64e7b0e1038f16fdb2103a71878e53"
  
) %>% 
  detailed_entries(
		what = Institution, with = Name, # Swapped for better format!
		when = Year, where = Where, 
		why = Details
	)
```

# Scientific Publications

```{r}
bibliography_entries("biblio.bib") %>%
  arrange(desc(issued))
```

# Awards

### *"Admeto Pettinari e Paolo Andreini" Scholarship* (01/10/2019){-}
Awarded by *Cassa di Sovvenzione e Risparmio per i dipendenti della Banca d'Italia* 
