---
name: Valerio
surname: Gherardi
#position: "Professor"
address: "Valencia, España"
phone: +34 681 904 907
profilepic: me-circle-cropped.png
www: vgherard.github.io
email: "vgherard@sissa.it"
twitter: ValerioGherardi
github: vgherard
linkedin: vgherard
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Theoretical Physicist from Italy, looking for Data Science / Engineering job opportunities."
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(dplyr)
```

# Description

My educational background provides me with a scientific and analytical mindset, which I love applying to problems and challenges coming from different areas. I have a wide experience with Data and Data Analysis, partly as a result of my physicist career, partly due to my passion for Machine Learning and Statistical Software Development.

During my PhD in Trieste I have had the privilege to study in an international, multicultural and multidisciplinary environment.
I love and get motivation from finding myself surrounded by people with heterogeneous backgrounds and life experiences. 

I am a fast learner and motivate worker, looking for job opportunities in Data Science / Engineering, starting from the end of my doctoral studies in October 2021.

# Education

```{r}
tribble(
	~ Name, ~ Year, ~ Institution, ~ Where, ~Details,
	"Laurea Triennale in Fisica", "2012-15", "Università La Sapienza", "Rome, Italy", "Final Grade: 110/110 cum laude",
	"Laurea Magistrale in Fisica", "2015-2017", "Università La Sapienza", "Rome, Italy", "Final Grade: 110/110 cum laude",
	"PhD in Theoretical Particle Physics", "2017-now", "International School for Advanced Studies (SISSA)", "Trieste, Italy", "Expected: September 2021"
	) %>%
	arrange(desc(Year)) %>%
	detailed_entries(
		what = Institution, with = Name, # Swapped for better format!
		when = Year, where = Where, 
		why = Details
	)
```

# Technical skills

**General.** Mathematical and statistical model building / Data Analysis / Scientific communication

**Programming languages.** R / C++ / Python / SQL / Wolfram / Fortran

**Data Science and Machine Learning.** Deep learning frameworks and APIs (TensorFlow, Keras, Trax) / Recurrent and Convolutional Neural Networks / Natural Language Processing / Classical Predictive Models

**Algorithmic coding.**  
Classical Data Structures (queues, stacks, heaps, trees, hash maps) / String algorithms / Graph and network algorithms / NP problems and SAT solvers 

**Software Development.**
Unit and functional testing / Version control (Git) / CI-CD / R Package Development

**Content creation.** RStudio Shiny / (R) Markdown / LaTeX 

# Certifications

```{r}
tribble(
  ~ Name, ~ Year, ~ Institution, ~ Where, ~Details,
  "Data Structures and Algorithms Specialization", "2021", "University of California San Diego", "Coursera.org", "Course description and certificate: https://coursera.org/share/4fe6c2e914585cb813c93488d20d8f52",
  "Natural Language Processing Specialization", "2021", "deeplearning.ai", "Coursera.org", "Course description and certificate: https://coursera.org/share/903e270df65d75737d6c884743509e84",
  "Deep Learning Specialization", "2020", "deeplearning.ai", "Coursera.org", "Course description and certificate: https://coursera.org/share/1a79776ec145f7d140c93b95281f5250",
  "Data Science Specialization", "2020", "Johns Hopkins University", "Coursera.org", "Course description and certificate: https://coursera.org/share/3d64e7b0e1038f16fdb2103a71878e53"
  
) %>% 
  detailed_entries(
		what = Institution, with = Name, # Swapped for better format!
		when = Year, where = Where, 
		why = Details
	)
```

# Personal Projects

### `r2r`



# Awards

# Publications

<!-- # Publications -->

<!-- ```{r} -->
<!-- bibliography_entries("biblio.bib") %>% -->
<!--   arrange(issued) -->
<!-- ``` -->

